### 2012-12-18 Krantz-v3/Chapters/chapter1/example_applications.tex
Auto-Backup Commit of All Projects

Many web-retails store and organize their catalog of products in a
mulitply-rooted hierarchy in addition to providing textual product descriptions 
for most products. Products can be discovered by users
through free-text search and product category exploration. Top-level
product categories are displayed on the front page of the website and lower
level categories can be discovered by choosing one of the top-level categories.
Products can exist in multiple locations in the hierarchy.

>>>>

Many web-retailers store and organize their catalog of products in a
mulitply-rooted hierarchy in addition to providing textual product descriptions 
for most products. Products can be discovered by users
through free-text search and product category exploration. Top-level
product categories are displayed on the front page of the website and lower
level categories can be discovered by choosing one of the top-level categories.
Products can exist in multiple locations in the hierarchy.

### 2012-12-18 Krantz-v3/Chapters/chapter1/inference.tex
Auto-Backup Commit of All Projects

The conditional posterior distribution of the regression coefficients is given by 
\begin{equation}
p(\boldsymbol\eta_{l}\mid\mathbf{z},\mathbf{a},\sigma) = \mathcal{N}(\hat{\boldsymbol\mu}_{l},\hat{\mathbf{\Sigma}})\label{eqn:regression_param_conditional}
\end{equation}
$\boldsymbol\eta_{l}$ for $l\in\mathcal{L}$. Given that $\boldsymbol\eta_{l}$
and $a_{l,d}$ are distributed normally, the posterior distribution
of $\boldsymbol\eta_{l}$ is normally distributed with mean $\hat{\boldsymbol\mu}_{l}$
and covariance $\hat{\mathbf{\Sigma}}.$% such that % (probably not the right place for this) We evaluated the model over various values of $\sigma$ where $\sigma=\left\{ 0.01,0.1,0.25,1,2\right\} $.
where
\begin{equation*}
\hat{\boldsymbol\mu}_{l}  =  \hat{\mathbf{\Sigma}}\left(\mathbf{1}\frac{\mu}{\sigma}+\bar{\mathbf{Z}}^{T}\mathbf{a}_{l}\right) \qquad \hat{\mathbf{\Sigma}}^{-1}  =  \mathbf{I}\sigma^{-1}+\bar{\mathbf{Z}}^{T}\bar{\mathbf{Z}}
.\end{equation*}
Here $\bar{\mathbf{Z}}$ is a $D\times K$ matrix
such that row $d$ of $\mathbf{\bar{Z}}$ is $\bar{\mathbf{z}}_{d}$, and $\mathbf{a}_{l}=[a_{l,1},a_{l,2},\ldots,a_{l,D}]^{T}$.  The simplicity of this conditional distribution follows from the choice of probit regression  \cite{Albert_Chib_1993}; the specific form of the update is a standard result from Bayesian normal  linear regression \cite{gelmanbda04}. 
%p\left(\boldsymbol\eta_{i_{l,c}}\mid\mathbf{z}_{1:D},\mathbf{a};\sigma\right)=\mathcal{N}\left(\boldsymbol\eta_{i_{l,c}}\mid\hat{\mu}_{i},\hat{\Sigma}_{i}\right)\end{equation}
%\[
%\[
%\subsection{$p\left(a_{l,d}\mid\mathbf{z},\mathbf{Y},\mathbf{\boldsymbol\eta}\right)$}
%and \textmd{$p\left(y_{m,i}\mid\mathbf{a}\right)$}}
%The auxiliary variables $a_{l,d}$ must be sampled for documents $d=1,\ldots,D$
%and $l\in\mathcal{L}_{d}$. The conditional posterior distribution
%of 
It also is a standard probit regression result that the conditional posterior
distribution of $a_{l,d}$ is a truncated normal
distribution~\cite{Albert_Chib_1993} (see also Section \ref{sec:probit_review}). 
\begin{eqnarray*}
\lefteqn{p\left(a_{l,d}\mid\mathbf{z},\mathbf{Y},\mathbf{\boldsymbol\eta}\right)}\\&\propto&
\begin{cases}
\exp\left\{ -\frac{1}{2}\left(a_{l,d}-\boldsymbol\eta_{l}^{T}\mathbf{\bar{z}}_{d}\right)\right\} \mathbb{I}\left(a_{l,d}y_{l,d}>0\right)\mathbb{I}(a_{l,d}<0) , & y_{\mathrm{pa}(l),d}=-1\\
\exp\left\{ -\frac{1}{2}\left(a_{l,d}-\boldsymbol\eta_{l}^{T}\mathbf{\bar{z}}_{d}\right)\right\} \mathbb{I}\left(a_{l,d}y_{l,d}>0\right) , & y_{\mathrm{pa}(l),d}=1\end{cases}\label{eqn:a_l_d}\end{eqnarray*}

>>>>

The conditional posterior distribution of the regression coefficients is given by 
\begin{equation}
p(\boldsymbol\eta_{l}\mid\mathbf{z},\mathbf{a},\sigma) = \mathcal{N}(\hat{\boldsymbol\mu}_{l},\hat{\mathbf{\Sigma}})\label{eqn:regression_param_conditional}
\end{equation}
$\boldsymbol\eta_{l}$ for $l\in\mathcal{L}$. Given that $\boldsymbol\eta_{l}$
and $a_{l,d}$ are distributed normally, the posterior distribution
of $\boldsymbol\eta_{l}$ is normally distributed with mean $\hat{\boldsymbol\mu}_{l}$
and covariance $\hat{\mathbf{\Sigma}},$% such that % (probably not the right place for this) We evaluated the model over various values of $\sigma$ where $\sigma=\left\{ 0.01,0.1,0.25,1,2\right\} $.
where
\begin{equation*}
\hat{\boldsymbol\mu}_{l}  =  \hat{\mathbf{\Sigma}}\left(\mathbf{1}\frac{\mu}{\sigma}+\bar{\mathbf{Z}}^{T}\mathbf{a}_{l}\right) \qquad \hat{\mathbf{\Sigma}}^{-1}  =  \mathbf{I}\sigma^{-1}+\bar{\mathbf{Z}}^{T}\bar{\mathbf{Z}}
.\end{equation*}
Here $\bar{\mathbf{Z}}$ is a $D\times K$ matrix
such that row $d$ of $\mathbf{\bar{Z}}$ is $\bar{\mathbf{z}}_{d}$, and $\mathbf{a}_{l}=[a_{l,1},a_{l,2},\ldots,a_{l,D}]^{T}$.  The simplicity of this conditional distribution follows from the choice of probit regression  \cite{Albert_Chib_1993}; the specific form of the update is a standard result from Bayesian normal  linear regression \cite{gelmanbda04}. 
%p\left(\boldsymbol\eta_{i_{l,c}}\mid\mathbf{z}_{1:D},\mathbf{a};\sigma\right)=\mathcal{N}\left(\boldsymbol\eta_{i_{l,c}}\mid\hat{\mu}_{i},\hat{\Sigma}_{i}\right)\end{equation}
%\[
%\[
%\subsection{$p\left(a_{l,d}\mid\mathbf{z},\mathbf{Y},\mathbf{\boldsymbol\eta}\right)$}
%and \textmd{$p\left(y_{m,i}\mid\mathbf{a}\right)$}}
%The auxiliary variables $a_{l,d}$ must be sampled for documents $d=1,\ldots,D$
%and $l\in\mathcal{L}_{d}$. The conditional posterior distribution
%of 
It also is a standard probit regression result that the conditional posterior
distribution of $a_{l,d}$ is a truncated normal
distribution~\cite{Albert_Chib_1993} (see also Section \ref{sec:probit_review}). 
\begin{eqnarray*}
\lefteqn{p\left(a_{l,d}\mid\mathbf{z},\mathbf{Y},\mathbf{\boldsymbol\eta}\right)}\\&\propto&
\begin{cases}
\exp\left\{ -\frac{1}{2}\left(a_{l,d}-\boldsymbol\eta_{l}^{T}\mathbf{\bar{z}}_{d}\right)\right\} \mathbb{I}\left(a_{l,d}y_{l,d}>0\right)\mathbb{I}(a_{l,d}<0) , & y_{\mathrm{pa}(l),d}=-1\\
\exp\left\{ -\frac{1}{2}\left(a_{l,d}-\boldsymbol\eta_{l}^{T}\mathbf{\bar{z}}_{d}\right)\right\} \mathbb{I}\left(a_{l,d}y_{l,d}>0\right) , & y_{\mathrm{pa}(l),d}=1\end{cases}\label{eqn:a_l_d}\end{eqnarray*}

### 2012-12-18 Krantz-v3/Chapters/chapter1/introduction.tex
Auto-Backup Commit of All Projects

Supervised LDA adds another per document observation, a label $y_d$.  It is modeled as being generated by a generalized linear model (GLM) $y_d | \bar{{\mathbf z}}_d, \boldsymbol\eta,\delta \sim \mathrm{GLM}(\bar{\mathbf{z}}_d,\boldsymbol\eta,\delta)$.  Brushing aside exponential family and GLM link function generalities, what SLDA does is regress labels against the empirical distributions of assigned topic indicator variables $\bar{\mathbf{z}}_d = \{\bar{z}_{1,d}, \ldots, \bar{z}_{K,d}\}$ where $\bar{z}_{k,d} = \frac{\sum_n \mathbb{I}(z_{n,d}=k)}{\sum_n \sum_j \mathbb{I}(z_{n,d}=j)}$ is the fraction of words assigned to topic $k$ ($\mathbb{I}(\cdot)$ is the indicator function that returns one if its argument is true).
If the document labels are real valued then one example choice for the regression relationship would be $y_d | {\bar{\mathbf z}}_d, \boldsymbol\eta \sim \mathcal{N}(\bar{\mathbf{z}}_d^T\boldsymbol\eta,\delta).$  Using an generalized linear model in the exponential family to parameterize this regression relationship allows for a wide variety of distributions over different kinds of label spaces to be represented in the same mathematical formalism.   A variational expectation maximization algorithm was proposed in \cite{BleiMcAuliffe2008} to learn model parameters.  Experimental results in \cite{BleiMcAuliffe2008}  showed both excellent out of sample label prediction and improved topics.  Topic improvement was measured by using the empirical topic proportions from SLDA  as features for external, discriminative approaches to label prediction.  Regression models built on SLDA topics outperformed the same built on LDA derived topics.

>>>>

Supervised LDA adds another per document observation, a label $y_d$.  It is modeled as being generated by a generalized linear model (GLM) $y_d | \bar{{\mathbf z}}_d, \boldsymbol\eta,\delta \sim \mathrm{GLM}(\bar{\mathbf{z}}_d,\boldsymbol\eta,\delta)$.  Brushing aside exponential family and GLM link function generalities, what SLDA does is regress labels against the empirical distributions of assigned topic indicator variables $\bar{\mathbf{z}}_d = \{\bar{z}_{1,d}, \ldots, \bar{z}_{K,d}\}$ where $\bar{z}_{k,d} = \frac{\sum_n \mathbb{I}(z_{n,d}=k)}{\sum_n \sum_j \mathbb{I}(z_{n,d}=j)}$ is the fraction of words assigned to topic $k$ ($\mathbb{I}(\cdot)$ is the indicator function that returns one if its argument is true).
If the document labels are real valued then one example choice for the regression relationship would be $y_d | {\bar{\mathbf z}}_d, \boldsymbol\eta \sim \mathcal{N}(\bar{\mathbf{z}}_d^T\boldsymbol\eta,\delta).$  Using a generalized linear model in the exponential family to parameterize this regression relationship allows for a wide variety of distributions over different kinds of label spaces to be represented in the same mathematical formalism.   A variational expectation maximization algorithm was proposed in \cite{BleiMcAuliffe2008} to learn model parameters.  Experimental results in \cite{BleiMcAuliffe2008}  showed both excellent out of sample label prediction and improved topics.  Topic improvement was measured by using the empirical topic proportions from SLDA  as features for external, discriminative approaches to label prediction.  Regression models built on SLDA topics outperformed the same built on LDA derived topics.
